# Intro to Data Science HW 7
##### Copyright Jeffrey Stanton, Jeffrey Saltz, and Jasmina Tacheva


```{r}
# Enter your name here: Kristan Rodriguez
```

### Attribution statement: (choose only one and delete the rest)


```{r}
# 1. I did this homework by myself, with help from the book and the professor.
# 2. I did this homework with help from the book and the professor.
# 3. I did this homework with help from <NErin> but did not cut and paste any code.
```

The chapter on **linear models** (“Lining Up Our Models”) introduces **linear predictive modeling** using the tool known as **multiple regression**. The term “multiple regression” has an odd history, dating back to an early scientific observation of a phenomenon called **“regression to the mean.”** These days, multiple regression is just an interesting name for using **linear modeling** to assess the **connection between one or more predictor variables and an outcome variable**. 


<br>In this exercise, you will **predict Ozone air levels from three predictors**.

A.	We will be using the **airquality** data set available in R. Copy it into a dataframe called **air** and use the appropriate functions to **summarize the data**. 


```{r}
air<- airquality
str(air)
#Import Packages
library(imputeTS)
library(tidyverse)
library(ggplot2)
library(RCurl)
library(jsonlite)
library(ggmap)
library(maps)
library(mapproj)
library(dplyr)
library(caret)
```

B.	In the analysis that follows, **Ozone** will be considered as the **outcome variable**, and **Solar.R**, **Wind**, and **Temp** as the **predictors**. Add a comment to briefly explain the outcome and predictor variables in the dataframe using **?airquality**.


```{r}
?airquality
# The variables were collected from May1, 1973- September 30, 1973. The mean Ozone are calculated in parts per billion, the Solar R. is the radiation in the frequency, the wind is the average speed of wind per miles an hour, and the Temp is the maximum daily temperature in degrees Fahrenheit.
```

C.	Inspect the outcome and predictor variables – are there any missing values? Show the code you used to check for that.


```{r}
is.na(air)
#There appears to be missing values in each variable except Month and Day
```

D.	Use the **na_interpolation()** function from the **imputeTS package** (remember this was used in a previous HW) to fill in the missing values in each of the 4 columns. Make sure there are no more missing values using the commands from Step C.


```{r}
air$Ozone<-na_interpolation(air$Ozone)
air$Solar.R<-na_interpolation(air$Solar.R)
air$Wind<-na_interpolation(air$Wind)
air$Temp<-na_interpolation(air$Temp)
```

E.	Create **3 bivariate scatterplots (X-Y) plots** (using ggplot), for each of the predictors with the outcome. **Hint:** In each case, put **Ozone on the Y-axis**, and a **predictor on the X-axis**. Add a comment to each, describing the plot and explaining whether there appears to be a **linear relationship** between the outcome variable and the respective predictor.


```{r}
ggplot(air, aes(x=Ozone, y=Solar.R)) + geom_point() + geom_smooth(method="lm")
#There does not seem to be a linear relationship between Ozone and Solar Radiation.
ggplot(air,aes(x=Ozone, y=Wind)) + geom_point() + geom_smooth(method="lm")
#There appears to be a slight linear relationship between the Ozone and Wind.
ggplot(air, aes(x=Ozone, y=Temp)) + geom_point() + geom_smooth(method="lm")
#There appears to be a direct relationship between Ozone and Temp.
```

F.	Next, create a **simple regression model** predicting **Ozone based on Wind**, using the **lm( )** command. In a comment, report the **coefficient** (aka **slope** or **beta weight**) of **Wind** in the regression output and, **if it is statistically significant**, **interpret it** with respect to **Ozone**. Report the **adjusted R-squared** of the model and try to explain what it means. 


```{r}
air1<-lm(formula = Ozone ~ Wind, data = air)
summary(air1)
#The slope is -4.5925, it is statistically significant as the p-value is 2.148e-11, this tells us that there is a direct correlation between how the wind effects the Ozone. The adjusted R squared is 0.2572, which means that the wind accounts for 25% of the Ozone change.
```

G.	Create a **multiple regression model** predicting **Ozone** based on **Solar.R**, **Wind**, and **Temp**.<br> **Make sure to include all three predictors in one model – NOT three different models each with one predictor.**


```{r}
air2<- lm(formula=Ozone ~ Solar.R + Wind + Temp, data= air)
summary(air2)
```

H.	Report the **adjusted R-Squared** in a comment – how does it compare to the adjusted R-squared from Step F? Is this better or worse? Which of the predictors are **statistically significant** in the model? In a comment, report the coefficient of each predictor that is statistically significant. Do not report the coefficients for predictors that are not significant.


```{r}
# The adjusted R squared value for the multiple regression is .4207 and the adjusted R squared a from F is .2527. The multiple regression is better than the single regression. In the model Wind and Temp are both statistically significant.The Coefficient Wind is -2.69669, and for Temp it is 1.530.
```

I.	Create a one-row data frame like this: 


```{r}
predDF <- data.frame(Solar.R=290, Wind=13, Temp=61)
```

 and use it with the **predict( )** function to predict the **expected value of Ozone**:


```{r}
predict(air2, predDF, type="response")
```

J.	Create an additional **multiple regression model**, with **Temp** as the **outcome variable**, and the other **3 variables** as the **predictors**. 

Review the quality of the model by commenting on its **adjusted R-Squared**.  


```{r}
air3<- lm(formula=Temp ~ Solar.R + Wind + Ozone, data= air)
summary(air3)
#The adjusted R squared is telling us that 40% of the temp is affected by the solar R., wind, and Ozone.
```
